---
title: "research_questions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(broom)
library(tidyverse)
library(ggplot2)
library(treemapify)
```
  
# Data preprocess
```{r, warning=FALSE}
data_automatic = read_csv("eventRegistry/rates/news_rates.csv") %>% 
  mutate(lexicon_type = "automatic")
data_manual_translated = read_csv("eventRegistry/rates/eventregistry_news_rates_manual_translated.csv") %>% 
  mutate(lexicon_type = "manual")
data = bind_rows(data_automatic, data_manual_translated)

data = data %>% mutate(country_location = if_else(source.uri == "br.sputniknews.com", "Brazil", country_location), 
                       topic = if_else(topic == "syria", "Syria", "Venezuela"), 
                       lang = if_else(lang == "deu", "ger", lang))

data_venezuela = data %>% 
  filter(topic == "Venezuela",
         opinative == FALSE, 
         lang != "ita") %>% 
  mutate(has_crisis = str_detect(body, " crisis | crise | Krise | chaos | situation | turmoil | crises | situação | emergencia humanitaria | tragedia | catástrofe | situación ")) # words define based on the similarity higher than 0.6 between them and "crisis"

data_syria = data %>% 
  filter(topic == "Syria",
         opinative == FALSE, 
         lang != "ita") %>% 
  mutate(has_war = str_detect(body, " war | guerra | Krieg | conflict | strife ")) # words define based on the similarity higher than 0.6 between them and "war"
data = bind_rows(data_syria, data_venezuela)

sources_venezuela = data %>% 
  filter(has_crisis == TRUE)

sources_syria = data %>% 
  filter(has_war == TRUE)

sources_both = sources_syria$source.uri %>% 
  intersect(sources_venezuela$source.uri)
sources_only_syria = sources_syria$source.uri %>% 
  setdiff(sources_venezuela$source.uri)
sources_only_venez = sources_venezuela$source.uri %>% 
  setdiff(sources_syria$source.uri)

data = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE) %>%
  mutate(publish_about = if_else(source.uri %in% sources_both, "Both", 
                                        if_else(source.uri %in% sources_only_venez, "Venezuela Crisis", 
                                                if_else(source.uri %in% sources_only_syria, "Syrian War", "Neither"))))
```

```{r}
data_manual_translated = read_csv("eventRegistry/rates/eventregistry_news_rates_manual_translated.csv")
data_manual_translated = data_manual_translated %>% 
  mutate(country_location = if_else(source.uri == "br.sputniknews.com", "Brazil", country_location), 
         topic = if_else(topic == "syria", "Syria", "Venezuela"), 
         lang = if_else(lang == "deu", "ger", lang))
```

# Data Description
## Date ranges
```{r}
data %>% group_by(lang, lexicon_type) %>% summarise(max_date = max(date), min_date = min(date))
```

## Number of news by language
```{r}
data %>% 
  group_by(lang, lexicon_type, variable) %>% 
  count()
```

## Number of news by language and topic
```{r}
news_lang_topic = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE, lexicon_type == "automatic") %>% 
  group_by(lang, topic) %>% 
  summarise(n = n()/5)

news_lang_topic %>% 
  ggplot(aes(area=n, subgroup=lang, fill=lang)) + 
  geom_treemap() +
  geom_treemap_text(aes(label=topic))+
  theme_bw() +
  theme(legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        legend.text = element_text(size=12),
        legend.title = element_text(size=12)
  )

ggsave("output/dataset_topic_distribution.pdf")
```

## Number of news containing "war" in syrian news article's body | Number of news containing "crisis" in venezuela news article's body
```{r}
war_syria = data_syria %>%
  filter(lexicon_type == "automatic") %>%
  group_by(lang) %>% 
  summarise(war = (sum(has_war == TRUE)/n()), no_war = 1-war) %>%
  reshape2::melt("lang") %>%
  mutate(topic = "Syria")

crisis_venezuela = data_venezuela %>%
  filter(lexicon_type == "automatic") %>%
  group_by(lang) %>% 
  summarise(crisis = sum(has_crisis == TRUE)/n(), no_crisis = 1-crisis) %>%
  reshape2::melt("lang") %>%
  mutate(topic = "Venezuela")

identifiers_in_syr_ven = bind_rows(war_syria, crisis_venezuela)

ggplot(identifiers_in_syr_ven, aes(x = lang, y = value)) +
  geom_col(aes(fill = factor(variable, levels=c("no_war","war","no_crisis","crisis"))), width = 0.7) + 
  facet_grid(. ~ topic) +
  theme_bw() +
  theme(axis.ticks.x = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        legend.title = element_blank(),
        axis.title = element_blank()
  )

ggsave("output/dataset_proof.pdf")
```

```{r}
news_by_country_lang = data %>% 
  filter(lexicon_type == "automatic") %>%
  group_by(country_location, lang) %>% 
  summarise(n = n()/5) %>%
  arrange(desc(n))
```


```{r}
news_by_country_lang_topic = data %>% 
  filter(lexicon_type == "automatic", has_war == TRUE | has_crisis == TRUE) %>%
  group_by(country_location, lang, topic) %>% 
  summarise(n = n()/5) %>%
  arrange(desc(n))
```

# Number of countries by language and topic
```{r}
countries_by_lang = data %>% 
  filter(lexicon_type == "automatic", has_war == TRUE | has_crisis == TRUE) %>%
  select(lang, topic, country_location) %>%
  distinct() %>% 
  group_by(lang, topic) %>% 
  summarise(n = n())
```

# Number of countries by topic
```{r}
distinct_countries = news_by_country_lang_topic$country_location %>% unique() %>% length()
```

# Distribution of news by country
```{r}
news_by_country_lang_topic %>% 
    filter(country_location != "-") %>% 
    ggplot(aes(area=n, fill=lang, subgroup=lang)) + 
    geom_treemap() +
    geom_treemap_text(aes(label=country_location)) +
    facet_wrap(topic ~ ., ncol = 2) + 
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position="bottom",
        legend.text = element_text(size=12),
        legend.title = element_text(size=12),
        strip.text = element_text(size=12)
    )

ggsave("output/country_distribution_by_topic.pdf", width = 5, height = 3)
```

# Distribution of news by country (barplot version)
```{r}
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

```{r}
news_by_country_lang_topic %>%
  filter(country_location != "-") %>%
  group_by(lang, topic) %>%
  top_n(10, n) %>% 
  ggplot() + 
  geom_bar(aes(x=reorder_within(country_location, n, n), y=n), stat = "identity") +
  scale_x_reordered() +
  coord_flip() +
  facet_wrap(topic ~ lang, ncol = 4, scales = "free") +
  theme_bw() + 
  theme(axis.title = element_blank())

ggsave("output/top_10_country_distribution_by_topic.png", width = 10, height = 5)
```

# Research Questions
## Proportion of remaining news per language
```{r}
total = data %>%
  filter(lexicon_type == "automatic") %>%
  group_by(lang, topic) %>% 
  summarise(total = n()/5)

remaining = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE, lexicon_type == "automatic") %>% 
  group_by(lang, topic) %>% 
  summarise(remaining = n()/5)

proportion = remaining %>% 
  inner_join(total) %>%
  mutate(prop = remaining/total)
```

## Experiment 1: Is there a significant subjectivities difference between the topics?
### As a whole (syria - venezuela)
```{r}
subj_topic = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE, lexicon_type == "automatic") %>% 
  group_by(variable) %>% 
  do(tidy(t.test(sub_mean~topic, data=., conf.int=0.99)))

subj_topic %>% 
  ggplot() +
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + 
  theme(axis.title = element_blank()) +
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw() +
  theme(legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.y = element_blank(),
        #axis.ticks.y = element_blank()
  )
```

### By language
```{r}
subj_topic_by_lang = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE) %>% 
  group_by(variable, lang, lexicon_type) %>% 
  do(tidy(t.test(sub_mean~topic, data=., conf.int=0.99)))

subj_topic_by_lang %>%
  filter(lexicon_type == "automatic") %>%
  ggplot() +
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + 
  theme(axis.title = element_blank()) +
  facet_wrap(. ~ lang) + 
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.text.x = element_text(size=12),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)

ggsave("output/subj_by_topic_lang.pdf", width = 5, height = 3)
```

#### By most publishing country of each language
```{r}
diff_subj_topic_by_country = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE, 
         country_location %in% c("Brazil","Germany","United States", "Venezuela")) %>% 
  group_by(variable, country_location, lexicon_type) %>% 
  do(tidy(t.test(sub_median~topic, data=., conf.int=0.99)))

diff_subj_topic_by_country %>% 
  filter(lexicon_type == "automatic") %>%
  ggplot() +
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + 
  theme(axis.title = element_blank()) +
  facet_wrap(. ~ country_location) + 
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.text.x = element_text(size=12),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)

ggsave("output/subj_by_country_representant.pdf", width = 5, height = 3)

```

### By news outlet
```{r}
library(gmodels)

data %>% 
  filter(lexicon_type == "automatic") %>%
  group_by(variable, publish_about) %>%
  do(tidy(gmodels::ci(.$sub_median, confidence = 0.99))) %>% 
  reshape::cast(variable+publish_about~names, mean) %>% 
  ggplot() +
  geom_errorbar(aes(publish_about, Estimate, ymin = get("CI lower"), ymax = get("CI upper"), color = publish_about)) + 
  facet_wrap(variable ~ .) +
  labs(x = "", y = "") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(.95, .10),
        legend.justification = c("right", "bottom"),
        legend.box.just = "right",
        legend.text = element_text(size=12),
        legend.title = element_text(size=12)
  ) 

ggsave("output/subj_by_country_representant.pdf", height = 4.5)
```

#### By news outlet's political bias

##### Data information
```{r}
n_total_outlets = data %>%
  filter(lexicon_type == "automatic") %>%
  select(source.uri) %>% 
  distinct() %>% 
  nrow()

n_stanced_outlets = data %>%
  filter(lexicon_type == "automatic") %>%
  filter(!is.na(stance)) %>% 
  select(source.uri) %>% 
  distinct() %>% 
  nrow()

n_news_by_country = data %>%
  filter(lexicon_type == "automatic") %>%
  filter(!is.na(stance)) %>%
  group_by(country_location) %>%
  summarise(n = n()/5) %>% arrange(desc(n))

n_news_by_country$n %>% sum()
```

##### Subjectivity difference in topics by Political Bias
```{r}
subj_topic_by_political_bias = data %>%
  filter(!is.na(stance)) %>% 
  group_by(variable, stance, lexicon_type) %>% 
  do(tidy(t.test(sub_median~topic, data=., conf.int=0.99)))

subj_topic_by_political_bias %>%
  filter(lexicon_type == "automatic") %>%
  ggplot() +
  geom_errorbar(aes(factor(stance), ymin = conf.low, ymax = conf.high)) + 
  facet_wrap(variable ~ .) + 
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        #legend.position="bottom",
        #legend.box = "vertical",
        #legend.key.size = unit(0.4, "cm"),
        #legend.position = c(1, -.00),
        #legend.justification = c("right", "bottom"),
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_x_discrete(limits=c("left","left_center","least", "right_center", "right"), labels=c("left" = "L","left_center" = "LC", "least" = "C", "right_center" = "RC", "right" = "R")) 

ggsave("output/topic_dif_by_political_stance.pdf",width = 5,height = 3)
```

#### Language, Country and Political Slant
```{r}
library(ggpubr)
subj_topic_by_lang = subj_topic_by_lang %>% mutate(group = "lang")
diff_subj_topic_by_country = diff_subj_topic_by_country %>% mutate(group = "country") %>% rename(country = country_location)
subj_topic_by_political_bias = subj_topic_by_political_bias %>% mutate(group = "stance")

p1 = diff_subj_topic_by_country %>% 
  filter(lexicon_type == "automatic") %>%
  ggplot() +
  geom_errorbar(aes(country, ymin = conf.low, ymax = conf.high, color=country)) + 
  theme(axis.title = element_blank()) +
  facet_grid(group ~ variable) +
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.text = element_text(size=12)
  ) + 
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)

p2 = subj_topic_by_lang %>% 
  filter(lexicon_type == "automatic") %>%
  ggplot() +
  geom_errorbar(aes(lang, ymin = conf.low, ymax = conf.high, color=lang)) + 
  theme(axis.title = element_blank()) +
  facet_grid(group ~ variable) + #, nrow = 1
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)

p3 = subj_topic_by_political_bias %>% 
  filter(lexicon_type == "automatic") %>%
  ggplot() +
  geom_errorbar(aes(factor(stance), ymin = conf.low, ymax = conf.high, color=stance)) + 
  facet_grid(group ~ variable) + 
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_x_discrete(limits=c("left","left_center","least", "right_center", "right"), labels=c("left" = "L","left_center" = "LC", "least" = "C", "right_center" = "RC", "right" = "R")) 

ggarrange(p1, p2, p3, ncol = 1, nrow = 3, common.legend = F)
ggsave("output/country_lang_stance.pdf",width = 5,height = 6)
```

```{r}
ggarrange(p1, p3, ncol = 1, nrow = 2, common.legend = F)
ggsave("output/country_stance.pdf",width = 5,height = 4)
```


#### Countries Subjectivities by topic
```{r}
subj_topic_by_country = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE, 
         country_location %in% c("United States","Brazil","Germany","Venezuela")
         ) %>% 
  group_by(variable, country_location, topic) %>% 
  do(tidy(ci(.$sub_median, confidence = 0.99))) %>%
  mutate(names = if_else(names == "CI lower", "conf.low", if_else(names == "CI upper", "conf.high", names))) %>%
  reshape::cast(country_location + variable + topic ~ names, mean) 

subj_topic_by_country %>% 
  ggplot() +
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high, color = topic), position = position_dodge2()) + 
  theme(axis.title = element_blank()) +
  facet_wrap(. ~ country_location, ncol = 2) +
 # geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.text = element_text(size=12)
  ) 

+
  scale_x_discrete(limits=c("Brazil","Germany","United States", "Venezuela"), labels=c("Brazil" = "BR","Germany" = "Ger", "United States" = "USA", "Venezuela" = "Ven"))  


ggsave("output/country_topic_mean_subjectivity.pdf",width = 5, height = 3)

```

#### Language - only news in english (automatic x manual translation)
```{r}
subj_topic_by_lang_eng = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE, lang == "eng") %>% 
  group_by(variable, lang, lexicon_type) %>% 
  do(tidy(t.test(sub_mean~topic, data=., conf.int=0.99))) %>% 
  mutate(group = "lang")

p5 = subj_topic_by_lang_eng %>% 
  filter(variable %in% c("pre","mod")) %>%
  ggplot() +
  geom_errorbar(aes(lang, ymin = conf.low, ymax = conf.high, color=lexicon_type), position = "dodge") + 
  theme(axis.title = element_blank()) +
  facet_grid(group ~ variable) + #, nrow = 1
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)

```

#### Political Slant - only news in english (automatic x manual translation)
```{r}
subj_topic_by_political_bias_eng = data %>%
  filter(!is.na(stance), lang == "eng") %>% 
  group_by(variable, stance, lexicon_type) %>% 
  do(tidy(t.test(sub_median~topic, data=., conf.int=0.99))) %>%
  mutate(group = "stance")

p6 = subj_topic_by_political_bias_eng %>%
  filter(variable %in% c("pre","mod")) %>%
  ggplot() +
  geom_errorbar(aes(stance, ymin = conf.low, ymax = conf.high, color=lexicon_type), position = "dodge") + 
  facet_grid(group ~ variable) + 
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_x_discrete(limits=c("left","left_center","least", "right_center", "right"), labels=c("left" = "L","left_center" = "LC", "least" = "C", "right_center" = "RC", "right" = "R"))

ggarrange(p4, p5, p6, ncol = 1, nrow = 3, common.legend = T, legend = "bottom")
ggsave("output/country_lang_stance_manual_lexicon.pdf", width = 5,height = 6)

```


#### Mean subjectivity by topic and Political Slant
```{r, warning=FALSE}
subj_topic_by_political_bias = data %>% 
  filter(!is.na(stance)) %>% 
  #mutate(stance = if_else(stance == "left_center", "left", if_else(stance == "right_center", "right", stance))) %>%
  group_by(variable, stance, topic) %>%
  do(tidy(ci(.$sub_median, confidence = 0.99))) %>%
  mutate(names = if_else(names == "CI lower", "conf.low", if_else(names == "CI upper", "conf.high", names))) %>%
  reshape::cast(stance + variable + topic ~ names, mean)

subj_topic_by_political_bias %>%
  ggplot() +
  geom_errorbar(aes(stance, ymin = conf.low, ymax = conf.high)) + 
  facet_grid(topic ~ variable, scales = "free") +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
  ) +
  scale_x_discrete(limits=c("left","least", "right"), labels=c("left" = "L", "least" = "C", "right" = "R"))
  #scale_x_discrete(limits=c("left","left_center","least", "right_center", "right"), labels=c("left" = "L","left_center" = "LC", "least" = "C", "right_center" = "RC", "right" = "R"))
```

## Experiment 2: Considering the news published in the most associated foreigner countries to each topic, is there significant subjectivity differences between topics related to the relation of the country to each topic? (i.e. USA is related to both venezuela and syria. Brazil is related only to Venezuela. UK is related only to Syria. Germany is non related to both)
```{r}

subj_topic_by_countries_association = data %>% 
  filter(has_war == TRUE | has_crisis == TRUE) %>% 
  filter(country_location %in% c("Switzerland")) %>%
  group_by(variable, country_location) %>% 
  do(tidy(t.test(sub_median~topic, data=., conf.int=0.99))) 

subj_topic_by_countries_association %>% 
  ggplot() +
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + #, color = topic_interest
  theme(axis.title = element_blank()) +
  facet_wrap(. ~ country_location, nrow = 2) + 
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw() +
  theme(legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.y = element_blank(),
        #axis.ticks.y = element_blank()
  )

ggsave("output/countries_relation_with_topic.pdf")
```

## Experiment 3: How Venezuela reports themselves compared to how the rest of the world reports venezuela
```{r}
ven_world_sub = data %>% 
  filter(has_crisis == TRUE, country_location != "-") %>% 
  mutate(country_location = if_else(country_location != "Venezuela", "World", country_location))%>%
  group_by(variable) %>% 
  do(tidy(t.test(sub_median~country_location, data=., conf.int=0.99)))

ven_world_sub %>% 
  ggplot() +
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + 
  theme(axis.title = element_blank()) +
  geom_hline(yintercept = 0, linetype = 2) +
  theme_bw() +
  theme(legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.y = element_blank(),
        #axis.ticks.y = element_blank()
  )

ggsave("output/venezuela_x_world.pdf")
```

# Difference between results with and without references values by topic
```{r, warning=FALSE}
subj_topic_lang = data %>%
  filter(has_war == TRUE | has_crisis == TRUE) %>%
  select(lang, url, dimension = variable, no_normalization = value, normalized = sub_median) %>%
  reshape2::melt(id=c("lang", "url", "dimension")) %>%
  mutate(variable = if_else(variable == "no_normalization", "No norm", "Norm")) %>%
  group_by(dimension, variable, lang) %>%
  do(tidy(ci(.$value, confidence = 0.99))) %>%
  mutate(names = if_else(names == "CI lower", "conf.low", if_else(names == "CI upper", "conf.high", names))) %>%
  reshape::cast(dimension + variable + lang ~ names, mean)

subj_topic_lang %>% 
  ggplot() +
  geom_errorbar(aes(lang, ymin = conf.low, ymax = conf.high, color = lang)) + 
  facet_grid(variable ~ dimension, scales = "free") +
  theme_bw()+
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0.0,0.01,0.02,0.03,0.04,0.7,0.72,0.74,0.76), labels = c("0.0","0.01","0.02","0.03","0.04","0.7","0.72","0.74","0.76"))

ggsave("output/normalization_stage_effect.pdf", width = 5, height = 3)
```


### Venezuela actors subjectivities
```{r}
filter_news_by_topic = function(dataset, to_find, to_find_not){
  dataset %>% filter(str_detect(title, to_find) & !str_detect(title, to_find_not))
}

guaido = filter_news_by_topic(data_venezuela, "Guaidó", "Maduro") %>% mutate(actor = "guaido")
maduro = filter_news_by_topic(data_venezuela, "Maduro", "Guaidó") %>% mutate(actor = "maduro")
venezuela_actors = bind_rows(guaido, maduro)
```

# Given news about Venezuela and its main actors
## Is there significant difference between the subjectivity level contained in news about its main actors (Guaido and Maduro)?
### By language in which the news is written
```{r}
dt_result = venezuela_actors %>% 
  group_by(variable, lang) %>% 
  do(tidy(t.test(sub_median~actor, data=., conf.level=0.99))) #guaido = estimate 1, maduro = estimate 2

dt_result %>% ggplot() + 
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + 
  facet_wrap(lang ~ ., scales = "free", ncol = 2) +
  theme_bw() +
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        #axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.text.x = element_text(size=12),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)
```

### By country
```{r}
most_publishing_countries = venezuela_actors %>% 
  filter(country_location != "-") %>%
  group_by(country_location) %>%
  summarise(n = n()/5) %>%
  arrange(desc(n)) %>%
  top_n(6,n)

venezuela_actors %>% group_by(variable, actor) %>% summarise(m = mean(sub_median))
  
venezuela_actors %>%   
  filter(country_location %in% most_publishing_countries$country_location) %>%
  group_by(variable, country_location) %>% 
  do(tidy(t.test(sub_median~actor, data=., conf.level=0.99))) %>%
  ggplot() + 
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + 
  facet_wrap(country_location ~ ., ncol = 3) +
  theme_bw() +
  theme(axis.title = element_blank(),
        legend.position="bottom",
        legend.box = "vertical",
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=12),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)

ggsave("output/venezuela_actors_by_country.pdf", width = 5, height = 3)
```

#### Guaido supporters x Maduro supporters
```{r}
guaido_sup = c("Albania", "Andorra", "Argentina", "Australia", "Austria", "Bahamas", "Belgium", "Brazil", "Bulgaria", "Canada", "Chile", "Colombia", "Costa Rica", "Croatia", "Czech Republic", "Denmark", "Dominican Republic", "Ecuador", "El Salvador", "Estonia", "Finland", "France", "Georgia", "Germany", "Greece", "Guatemala", "Haiti", "Honduras", "Hungary", "Iceland", "Ireland", "Israel", "Japan", "Latvia", "Lithuania", "Luxembourg", "Malta", "Marshall Islands", "Micronesia", "Montenegro", "Morocco", "Netherlands", "North Macedonia", "Panama", "Paraguay", "Peru", "Poland", "Portugal", "Romania", "Slovenia")

maduro_sup = c("Belarus", "Bolivia", "Cambodia", "China", "Cuba", "Dominica", "Equatorial Guinea", "Iran", "Laos", "Nicaragua", "North Korea", "Palestine", "Russia", "Saint Kitts and Nevis", "Saint Vincent and the Grenadines", "Serbia", "South Africa", "Suriname", "Syria")

venezuela_actors = venezuela_actors %>% mutate(support = if_else(country_location %in% guaido_sup, "Guaido", 
                                              if_else(country_location %in% maduro_sup, "Maduro", "Neutral")))


support_result = venezuela_actors %>% 
  group_by(variable, support) %>% 
  do(tidy(t.test(sub_median~actor, data=., conf.level=0.99))) #guaido = estimate 1, maduro = estimate 2

support_result %>% ggplot() + 
  geom_errorbar(aes(variable, ymin = conf.low, ymax = conf.high)) + 
  facet_wrap(. ~ support) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.title.x = element_blank(),
        axis.text = element_text(size=12),
        strip.text = element_text(size=12)
  ) +
  scale_y_continuous(breaks = c(0), labels = c("0.0")) +
  geom_hline(yintercept = 0, linetype = 2)

ggsave("output/subjectivity_by_actors_supportes.pdf")
```